PREPRINT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- PREPRINT.

### 2024-03-12 index.qmd
fig updated

## Drone Data

At each location, a DJI Matrice 200 quadcopter drone equipped with a Micasense RedEdge Dual MX multispectral camera was flown to take 1.2 million pixel reflectance photographs with ten spectral bands, from 444 nm (blue) to 840 nm (near infrared, NIR). To ensure consistent lighting conditions across flight paths, the drone's trajectory was aligned to maintain a solar azimuth angle of 90 degrees. An overlap of 70% and 80% (side and front respectively) between each image was set for each flight. A downwelling light sensor (DLS2) was used to acquire irradiance data concomitantly with the camera measurements. Raw data were calibrated in reflectance using a calibration panel reflective at \~50% provided by the manufacturer. A structure-from-motion photogrammetry software (Agisoft Metashape) was used to process images to obtain multispectral orthomosaics of each flight. The workflow for orthomosaicking was the same for every flight. First, tying key points were detected inside of each image and between overlapping images in order to obtain a sparse point cloud. This cloud was cleaned using reprojection accuracy metric in order to remove noisy points. A dense point cloud was then produced using a structure from motion algorithm. A surface interpolation of this dense point cloud was made to obtain a digital surface model (DSM), used to reconstruct the multispectral ortho-image. Across all sites, flights were made at two different altitudes : 12 m or/and 120 m. Low altitude drone flights produce ortho-images with a very high spatial resolution (8 mm per pixel), making it efficient to visually distinguish between the various types of vegetation. High altitude fights on the other hand allow to cover large areas and produced images with a pixel size of 80 mm (@tbl-flights).

@@

@@

## Intertidal vegetation mapping

@@

@@

>>>>

### Drone acquisition

At each location, a DJI Matrice 200 quadcopter drone equipped with a Micasense RedEdge Dual MX multispectral camera was flown to take 1.2 million pixel reflectance photographs with ten spectral bands, from 444 nm (blue) to 840 nm (near infrared, NIR). To ensure consistent lighting conditions across flight paths, the drone's trajectory was aligned to maintain a solar azimuth angle of 90 degrees. An overlap of 70% and 80% (side and front respectively) between each image was set for each flight. A downwelling light sensor (DLS2) was used to acquire irradiance data concomitantly with the camera measurements. Raw data were calibrated in reflectance using a calibration panel reflective at \~50% provided by the manufacturer. Across all sites, flights were made at two different altitudes : 12 m or/and 120 m. (@tbl-flights).

@@

### Ground Control Points

@@

## Drone Processing

A structure-from-motion photogrammetry software (Agisoft Metashape) was used to process images to obtain multispectral orthomosaics of each flight. The workflow for orthomosaicking was the same for every flight. First, tying key points were detected inside of each image and between overlapping images in order to obtain a sparse point cloud. This cloud was cleaned using reprojection accuracy metric in order to remove noisy points. A dense point cloud was then produced using a structure from motion algorithm. A surface interpolation of this dense point cloud was made to obtain a digital surface model (DSM), used to reconstruct the multispectral ortho-image. Low altitude drone flights produce ortho-images with a very high spatial resolution (8 mm per pixel), making it efficient to visually distinguish between the various types of vegetation. High altitude fights on the other hand allow to cover large areas and produced images with a pixel size of 80 mm (@tbl-flights).

## General Workflow

@@

Variable Importance Plots (VIP) serve as a method to identify which predictors are important for predicting a specific class. This is achieved by repeatedly predicting the same dataset while shuffling one predictor at a time. The benchmark score obtained after each iteration is then compared to the benchmark score obtained without shuffling any variables. The greater the difference between these two benchmark values, the more important the variable is for the model (@WEI2015399).

@@

The key aspect of the workflow adopted in the present study is the mapping of specific areas at two different altitudes (12m and 120m), resulting in two distinct resolutions for the same area (8mm and 80mm). The predictions made on the high-resolution flight can be used to estimate the percent cover of each vegetation class for every pixel of the lower resolution flight. Consequently, for each pixel of the high-altitude flights, percent covers of each vegetation class were obtained, and a kernel density plot was generated. This plot provides a visual representation of the behavior of the model in different vegetation percent cover scenarios.
